---
title: "MICE Encoding SubEmoMemScore Variance"
author: Kyle Kurkela
date: '`r Sys.Date()`'
output: 
  html_notebook:
    code_folding: show
    theme: cosmo
    toc: yes
    toc_float: true
---

```{r setup, message=FALSE, echo=FALSE}
library('tidyverse')
```

# Read in Data

Recursively read in the encoding `task-encoding*.tsv` files from `~/sourcedata/`, excluding that one run from that one subject that has two noise columns for some reason...

```{r load, warning=FALSE, message=FALSE}

datapath    <- '~/Desktop/sourcedata/'
datafiles   <- list.files(datapath,pattern='.*task-encoding.*\\.tsv$',full.names=TRUE,recursive=TRUE)
numCols     <- lapply(lapply(datafiles,read.delim), ncol)
numColsFilt <- numCols == 17
datafiles   <- datafiles[numColsFilt]
df          <- do.call(rbind, lapply(datafiles,read.delim))

```

Add a `subject` and `run` column to the data by extracting this information from the `datafiles` names

```{r add_subjectID_column}

matches      <- regexpr("sub-s[0-9]{3}", datafiles)
subjectIDs   <- regmatches(datafiles, matches)

matches      <- regexpr("run-[0-9]{2}", datafiles)
runIDs       <- regmatches(datafiles, matches)

df$subject   <- rep(subjectIDs, each = 32)
df$run       <- rep(runIDs, each = 32)

```

# Tidy Up the Data

Tidy up the data, making things factors that need to be factors, etc.

```{r tidyup}
df %>%
  select(subject, run, Condition, SubsequentEmoMemoryResp, SubsequentEmoMemory, SubEmoMemScore) %>%
  mutate(
    Emotion                 = ifelse(grepl('neg', Condition), "Negative", 
                                     ifelse(grepl('neu', Condition), "Neutral", NA)),
    Emotion                 = factor(Emotion, levels = c("Negative", "Neutral")),
    SubsequentEmoMemory     = as.logical(SubsequentEmoMemory),
    SubEmoMemScore          = factor(SubEmoMemScore, levels = c("NaN", "1", "2", "3", "4")),
    subject                 = factor(subject),
    run                     = factor(run)
  ) -> tidy.df
```

# Breakdown

Lets Breakdown the variance in the SubEmoMemScore across `subject`s and `Emotion`s

```{r}
tidy.df %>%
  ggplot(aes(x = subject, fill = SubEmoMemScore)) +
  geom_bar(position = "stack", width = .8) +
  facet_grid(~Emotion) +
  theme(axis.text.x = element_blank()) +
  xlab("Subjects") +
  ylab("Trial Count") +
  ggtitle("Subsequent Emotional Memory Score Variance", subtitle = "Among MICE fMRI Subjects") +
  labs(caption = "NaN = Subsequent NRs\nRed Shades = Incorrect, Blue Shades = Correct") +
  scale_fill_manual(values=c("#fecc5c", "#fd8d3c", "#e31a1c", "#a6bddb", "#2b8cbe"))
```

*Conclusion:*  
It looks like there is NOT a lot of variance in the Subsequent Emotional Memory Score Parametric Modulator for many subjects... 

# Examining non-HC Correct Trials cut-offs

How many subjects would we lose if we used a cut-off of at least 10 non-HC Correct Trials?

```{r}
tidy.df %>%
  mutate(
    SubEmoMemScore = factor(SubEmoMemScore, levels = c("4", "NaN", "1", "2", "3"))
  ) %>%
  ggplot(aes(x = subject, fill = SubEmoMemScore)) +
  geom_bar(position = "stack", width = .8) +
  facet_grid(~Emotion) +
  theme(axis.text.x = element_blank()) +
  xlab("Subjects") +
  ylab("Trial Count") +
  ggtitle("Subsequent Emotional Memory Score Variance", subtitle = "Among MICE fMRI Subjects") +
  labs(caption = "NaN = Subsequent NRs\nRed Shades = Incorrect, Blue Shades = Correct") +
  scale_fill_manual(values=c("#2b8cbe", "#fecc5c", "#fd8d3c", "#e31a1c", "#a6bddb")) + 
  geom_hline(yintercept = 10, color = "black")
```

Note: The Light Blue + Red-ish colors need to exceed the black line for BOTH negative AND neutral.

## Block Level Score Distribution

```{r block_level}
tidy.df %>%
  group_by(subject, run) %>%
  mutate(miniblock = factor(rep(1:(n()/4), each = 4)),
         SubEmoMemScore = as.numeric(SubEmoMemScore)) -> tidy.df

tidy.df %>%
  group_by(subject, run, miniblock) %>%
  summarize(Emotion = unique(Emotion),
            BlockLevelSubEmoMemScore = sum(SubEmoMemScore)) %>%
  mutate(BlockLevelSubEmoMemScore = factor(BlockLevelSubEmoMemScore,
                                           levels = (c("20", "19", "18", "17", "16", "15", 
                                                      "14", "13", "12", "11", "10", "9", 
                                                      "8", "7", "6", "4")))) %>%
  ggplot(aes(x = subject, fill = BlockLevelSubEmoMemScore)) +
  geom_bar(position = "stack") + facet_grid(~Emotion) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values=rev(c('#fff7ec','#fee8c8','#fdd49e','#fdbb84','#fc8d59',
                                 '#ef6548','#d7301f','#b30000','#7f0000','#edf8e9',
                                 '#bae4b3','#74c476','#238b45','#ece7f2','#a6bddb',
                                 '#2b8cbe'))) +
  ylab("Block Count") +
  xlab("Subjects") +
  ggtitle("Subsequent Emotional Memory Score Variance", subtitle = "Among MICE fMRI Subjects, by Miniblock") +
  labs(caption = "Red Shades = Low Scoring Miniblocks\nBlue/Green Shades = High Scoring MiniBlocks")
  
```

